---
title: "Assignment 3"
author: "Elizabeth Miller"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part I

Load the data file called ‘car_data.csv’. This data contains information about cars and motorcycles listed on CarDekho.com

```{r, warning = F, echo = F}
library(tidyverse)
library(plotly)
library(GGally)
library(corrplot)
```

```{r}
car <- read_csv("car_data.csv")
concealed <- read_csv("concealed_carry.csv")
```

1.  Create a correlogram among selling price, number of kilometers driven, and year the car was bought using the appropriate function in the GGally package. (6 pts)

```{r}
car %>%
  select(selling_price, km_driven, year) %>%
  ggpairs()
```


2.  Plot the relationship between the selling price and year for the automatic and manual cars on the same plot. The points on the graph should:

    1.  be colored based on transmission

    2.  the tooltip should indicate the year, selling price, and transmission type.
    
```{r}
p <- car %>%
  mutate(myText = paste("Transmission type: " , transmission,
                        "\nYear:", year,
                        "\nSelling price:", scales::comma(selling_price))) %>%
  ggplot(aes(x = year, y = selling_price, 
             color = transmission, 
             text = myText)) +
  geom_point(alpha = 0.7) +
  scale_y_continuous(labels = scales::comma)

options(scipen=999)

ggplotly(p, tooltip="text")
```

